---
title: "PM566 Final Project"
author: "Ruowen Wang"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

This is my PM566 Final Project website.


```{r setup, message=FALSE, echo=FALSE, warning=FALSE}
library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)
# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = TRUE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px")
```

```{r load-data, echo=FALSE}
source("process_COVID_data.R")
```

```{r plot1, class.source="code-r-small", echo=FALSE}
p1_scatter <- cv_states_today %>% 
  plot_ly(x = ~pop_density, y = ~deathsper100k,
          type = 'scatter', mode = 'markers', color = ~state,
          size = ~population, sizes = c(5, 70), marker = list(sizemode='diameter', opacity=0.5),
          hoverinfo = 'text',
          text = ~paste( paste(state, ":", sep=""), paste(" Cases per 100k: ", per100k, sep="") , paste(" Deaths per 100k: ",
                        deathsper100k, sep=""), sep = "<br>")) %>%
  layout(title = "Population-normalized COVID-19 deaths vs. population density",
                  yaxis = list(title = "Deaths per 100k"), xaxis = list(title = "Population Density"),
         hovermode = "compare")

# filter out "District of Columbia"
cv_states_today_scatter <- cv_states_today %>% filter(state!="District of Columbia")

p2_scatter <- cv_states_today_scatter %>% 
  plot_ly(x = ~pop_density, y = ~deathsper100k,
          type = 'scatter', mode = 'markers', color = ~state,
          size = ~population, sizes = c(5, 70), marker = list(sizemode='diameter', opacity=0.5),
          hoverinfo = 'text',
          text = ~paste( paste(state, ":", sep=""), paste(" Cases per 100k: ", per100k, sep="") , paste(" Deaths per 100k: ",
                        deathsper100k, sep=""), sep = "<br>")) %>%
  layout(title = "Population-normalized COVID-19 deaths vs. population density",
                  yaxis = list(title = "Deaths per 100k"), xaxis = list(title = "Population Density"),
         hovermode = "compare")
```

## lab-12 {.tabset}

### Figure 1

```{r echo=FALSE}
p1_scatter
```

### Figure 2

```{r echo=FALSE}
p2_scatter
```



## Assignment-5 {.tabset}

### Figure 1

- Find which states have the total confirmed cases on Sep/28/2020 which are over 200,000.

```{r message=FALSE, echo=FALSE, warning=FALSE, results='hide',fig.show='hide'}
library(data.table)
library(leaflet)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(knitr)
library(usmap)
library(scales)
library(RColorBrewer)
# Read in data
sdi <- data.table::fread("/Users/christina/Desktop/Social distancing index_ST.csv")
totcases <- data.table::fread("/Users/christina/Desktop/us_state_confirmed_case.csv")
# Delete the extra columns. I want to see the data of the same period in both data set. So I keep the period from Jan/21/2020 to Sep/28/2020.
sdi1<- sdi[ ,-c(4:23)]
sdi1<- sdi1[ ,-c(1)]
totcases1<- totcases[ ,-c(265:272)]
totcases1<- totcases1[ ,-c(3:12)]
# Find which states have the total confirmed cases on Sep/28/2020 which are over 200,000.
tot0928<-totcases1[ ,c(2,254)]
tot0928a<-tot0928[`2020-09-28`>200000,]
tot0928a$NAME<-reorder(tot0928a$NAME, -tot0928a$`2020-09-28`)
p1 = ggplot(tot0928a,aes(x=NAME, y=`2020-09-28`, fill=NAME))+geom_bar(stat = 'identity')
```

```{r echo=FALSE}
p1
```

### Figure 2

- Compare the social distance index with the total confirmed cases in the states which are over 200,000.
- From the following biaxial chart, in the 9 states with more than 200,000 confirmed infected people. If we set the social distance lager than 35 as the long social distance Here are 4 states follow patterns are shown: those with fewer infected people have a longer social distance, such as New York and New Jersey; the number of infected people is higher in states with shorter social distance, such as California, Florida and Texas.

```{r echo=FALSE}
# Compare the social distance index with the total confirmed cases in the states which are over 200,000.
sdistate = sdi1[c(3,5,10,11,14,31,33,34,44),2]
sdistate1 = sdi1[c(3,5,10,11,14,31,33,34,44),3:254]
sdistatez = sdistate
meandis = apply(sdistate1,1,mean)
sdistatez$name = sdistate
sdistatez$meandis = meandis
total = tot0928a$`2020-09-28`
sdistatez$total = total

par(mar = c(5, 5, 3, 4)+0.1) 
bar = barplot(sdistatez$total,ylab="total",
col="orange",col.axis="orange",col.lab="orange")
mtext(sdistatez$name,side=1,line=1,at=bar,cex=0.8,col="black")
par(new=T)
plot(bar,sdistatez$meandis,axes=F,xlab="",ylab=" ",col="red",type="o")
axis(4,col="red",col.ticks="red",col.axis="red")
```

### Figure 3

- Plot the mean values of social distance index of the 9 states on the map.
- The states in grey color are those who have total confirmed cases lower than 200,000, which I did not calculate the mean values.
- The states in blue color are those who have total confirmed cases over than 200,000, which I have calculated the mean values before. The dark blue indicates the higher mean of social distance index, the light blue indicates the lower mean of social distance index.

```{r echo=FALSE}
library(usmap)
sdistatem = as.data.frame(sdistatez)
names(sdistatem)[2] <- "state"
p3 = plot_usmap('states', data =sdistatem, values ='meandis')+
scale_fill_continuous(low = "light blue", high = "dark blue", guide = FALSE)
```

```{r echo=FALSE}
p3
```
